%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
\begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Haowen} \headerlastnamestyle{Yan} \\
	\vspace{2mm}
	{\faEnvelope\ yanhw7@mail2.sysu.edu.cn} | {\faMobile\ 13790024428} | {\faMapMarker\ Guangdong, China} \\
	{\faLink\ whY-note.github.io} | {\faGithub\ https://github.com/whY-note}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Biography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Biography}

% 我是严浩文，一名中山大学计算机科学与技术专业的大三本科生。
% 目前我参与了机械臂遥操作，极快模型预测控制器，5级流水线CPU设计，基于RISC-V的操作系统设计等项目，并在相关领域积累了丰富的经验。
% 我的研究兴趣是：具身智能，机器人，强化学习，最优控制。

I am Haowen Yan, a third-year undergraduate student majoring in Computer Science and Technology at Sun Yat-sen University.

I have participated in projects including robotic arm teleoperation, ultra-fast model predictive controller (MPC), 5-stage pipelined CPU design, and RISC-V-based operating system development, gaining substantial experience in these areas.

My research interests include Embodied AI, Robotics, Reinforcement Learning, and Optimal Control.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{Bachelor in Computer science}
	{Sun Yat-Sen University}
	{Guangdong, China}
	{Sept 2023 – Now}
	{GPA: 4.3397/5.0}

\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Course Grades
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Course Grades}
The average grade for core major courses is above 90, with some courses exceeding 95.
	
Mathematics Analysis II (98), Probability and Statistics (96), Machine Learning (98), Data Structures (98)


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Projects}
\begin{cventries}
	\cventry
	{\begin{itemize}[leftmargin=*]
		\item Implemented teleoperation of an existing robotic arm using Meta Quest 3S.
		\item In many existing teleoperation systems, the robot motion is affected by the head-mounted display (HMD): even when the controller remains stationary, movement of the HMD alone can cause unintended robot motion. 
		\item By introducing the initial pose of the HMD as a reference frame, this work eliminates the influence of HMD motion, thereby improving system stability and control accuracy.
	\end{itemize}
	}
	{Teleoperation of a robotic arm}
	{Python}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{\begin{itemize}[leftmargin=*]
		\item Deployed a hardware-software co-accelerated MPC on a UAV and tested its performance. 
		\item Modeled UAV dynamics and verified state-space equations via MATLAB simulations. 
		\item Programmed the MPC on an FPGA and controlled UAV flight through ROS + Gazebo simulation.
	\end{itemize}
	}
	{Ultra-Fast Model Predictive Controller (MPC)}
	{C/C++, Python}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{\begin{itemize}[leftmargin=*]
		\item Designed a single-cycle CPU and a 5-stage pipelined CPU, with all hazards (data, structural, and control) resolved in hardware. 
		\item Implemented both CPUs in Verilog, simulated and debugged them, and deployed on an FPGA development board.
	\end{itemize}
	}
	{A single-cycle CPU and a 5-stage pipelined CPU based on the MIPS instruction set.}
	{Verilog, Python}
	{https://github.com/whY-note/PipelineCPU}
	{}
	
	\vspace{-5mm}
	\cventry
	{
	\begin{itemize}[leftmargin=*]
		\item Developed an OS on RISC-V, supporting \textasciitilde{}90 system calls; participated in the Operating System Design Competition.
		\item Designed and implemented an RISC-V-based operating system with nearly 90 system calls, competing in the OS Design Competition.
	\end{itemize}
	}
	{Operating System Based on the RISC-V Instruction Set}
	{}
	{}
	{}
	
	\vspace{-5mm}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Honours and Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Honours and Awards}
\begin{cvhonors}
	\cvhonor
	{National Scholarship}
	{}
	{}
	{2024}
	\cvhonor
	{National Scholarship}
	{}
	{}
	{2025}
	\cvhonor
	{Third Prize, Kernel Implementation Track, National College Student Operating System Design Competition (China)}
	{Implemented an operating system on the RISC-V instruction set, supporting nearly 90 system calls.}
	{}
	{Aug 2025}
	\cvhonor
	{First Prize, Guangdong Division, National College Student Mathematics Competition (China)}
	{}
	{}
	{Nov 2024}
	\cvhonor
	{Second Prize, Guangdong Division, “Shenzhen Cup” Mathematical Modeling Competition (China)}
	{}
	{}
	{Dec 2024}
	\cvhonor
	{Third Prize, Guangdong Division, National College Student Mathematical Modeling Competition (China}
	{}
	{}
	{Oct 2024}
	\cvhonor
	{H Award, Mathematical Contest in Modeling (MCM), USA}
	{}
	{}
	{May 2025}
	\cvhonor
	{Second Prize, South China Division, MathorCup Mathematical Modeling Competition (China)}
	{}
	{}
	{Apr 2024}
\end{cvhonors}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{%
        \begin{tabular}{ l l }
		English: \quad & {\skill{CET-4(621), CET-6(556)}} \\
        Programming:\quad & {\skill{Python, C/C++, Matlab, Rust, Verilog}} \\
        Softwares:\quad & {\skill{Linux, Mujoco, ROS, Git}} \\
        Trait:\quad & 
        {\skill{\begin{minipage}[t]{1.0\linewidth}
            \begin{itemize}[leftmargin=*]
                \item \textbf{Innovative:} Designed a 5-stage pipelined CPU with all data, structural, and control hazards handled entirely by hardware.
                \item \textbf{Diligent and Detail-Oriented:} Explored the underlying logic of concepts while studying Mathematical Analysis and Linear Algebra, delving into each detail.
                \item \textbf{Self-Learner:} Independently studied Reinforcement Learning, Optimal Control, Introduction to Robotics, and other advanced topics.
                \item \textbf{Persistent and Hardworking:} Committed to completing every task thoroughly, willing to endure challenges and take on less glamorous work.
            \end{itemize}
        \end{minipage}}} \\
        \end{tabular}%
    }}
	{}
	{}
	{}
\end{cventries}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Contact Me
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Contact Me}
\begin{itemize}
	\item \textbf{Email:}  yanhw7@mail2.sysu.edu.cn
	\item \textbf{Phone:} 13790024428
	\item \textbf{Homepage:} whY-note.github.io
	\item \textbf{Github:} https://github.com/whY-note
	\item \textbf{WeChat:} Y13790024428
\end{itemize}

\end{document}
